---
title: "How To Make A Billion"
output: github_document
---

Data Source Link: 

https://www.kaggle.com/datasets/nelgiriyewithana/billionaires-statistics-dataset

# Data Prep Tasks:

```{r}
data <- read.csv("data/Billionaires Statistics Dataset.csv") 
str(data)   
```


```{r}
data$gdp_country <- gsub(pattern = ",|\\$|\\s",
                         replacement ="",
                         data$gdp_country)

data$gdp_country <- as.numeric(data$gdp_country)
```

Used 'gsub' to remove commas in my GDP country column, then changed it to numeric just so if I can make any calculations in future.

```{r}
library(stringr)

data$gender <- str_extract(data$gender, "[FM]")
```


```{r}
library(lubridate)
data$DOB <- as.Date(data$birthYear,data$birthMonth,data$birthDay)
str(data)
```

Loaded lubridate because this package also helps in doing a lot of manipulations with Dates. Then added a column called DOB while changing its class by date.

# Data Analytical Tasks

a. Which industries are most common among billionaires?
   
```{r}
library(ggplot2)

viz_1 <- ggplot(data, aes(x = finalWorth, y = category)) +
  geom_point(color = "black") +
labs(title = "Which industries are most common among billionaires?") +
  theme_minimal() 
```

Created a scatter plot to check "Which industries are most common among billionaires."


b. How has the source of wealth evolved over time?
   
```{r}

viz_2 <- ggplot(data, aes(x = birthYear, y = finalWorth))+
  geom_line(color = "black") +
    labs(title = "How has the source of wealth evolved over time?") +
  theme_minimal()

viz_1
viz_2
library(patchwork)
viz_1 + viz_2
viz_1 / viz_2
```
   
Same here, I wanted to know the relation between time and wealth. So, I created a line graph.

New thing here is I used patchwork to combine the above two plots. First I wanted to do side by side then I saw the information is congested and not looking nice so I made up and down by using viz 1/viz 2 syntax.
   
c. Are there any specific trends in the sources of wealth for self-made billionaires?
   
```{r}
library(ggdark)
ggplot(data,
       aes(x = status, y = finalWorth)) +
  geom_boxplot() +
  scale_color_brewer(type = "qual", palette = "Set2") +
    labs(title = "D: Entrepreneur, U: Inherited, N: Investment, E: Real Estate, R: Others") +
  dark_theme_minimal() 
```

New thing here😄 

I used ggdark here to get dark themed plots. Created a box and whisker plots to summarise and see the distribution of the data. Then I reverted into the geom defaults because when ggdark is used the defaults are changed.So, we always should definitely change it to default after using ggdark.

```{r}
invert_geom_defaults()
```

